---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# plot

<!-- badges: start -->
<!-- badges: end -->

This is an R package I use to help make pen-plotter art using R. Since my pen plotter uses G-code, the package has some function to turn a dataframe containing cartesian coordinates into G-code for plotting. It also includes functions to help preview art before plotting.

## Installation

You can install the development version of plot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("robbrotherton/plot")
```

## Example

Let's make some art.

```{r}
library(plot)

# It's a triangle

df <- data.frame(x = c(10, 100, 200, 10),
                 y = c(60, 230, 60, 60))

```

Let's see how it might look in a frame.

```{r}

frame(df)

```

Now we can turn the data into g-code to use with the pen plotter.

```{r}

plotting_time(df)

```

```{r, eval = FALSE}
write_gcode(df, filename = here::here("test.gcode"))

```
